SoK: The Evolution of Defenses Against Web Application Attacks

### 2014-10-28 docs/questioning.tex
ISR draft ready

Here we analyze the {\sc tba} different protection approaches.

@@

{\it {\sc sql}rand}~\cite{BK04} is based on {\sc isr}
to detect {\sc sql} injections in the following manner:
initially, it allows programmers to create {\sc sql} statements
using randomized instructions instead of standard keywords.
The modified queries are either reconstructed at runtime using
the same key that is inaccessible to the malicious user,
or the user input is tagged with delimiters that allow
an augmented {\sc sql} grammar to detect the
attack.

In the case of {\sc xss} attacks that are based on JavaScript,
consider a {\sc xor} function that encodes all JavaScript source of a web
page on the server-side and then, on the client-side, the web browser decodes the
source by applying the same function again.
Variations of this approach include:
{\it Noncespaces}~\cite{GC09} and {\it x{\sc js}}~\cite{APKLM10}.

>>>>

Here we analyze the {\sc tba} different protection approaches.
Note that most mechanisms that belong to this category have
not been extensively tested in terms of diagnostic performance.

@@

{\it {\sc sql}rand}~\cite{BK04} is based on {\sc isr}
to detect {\sc sql} injections in the following manner:
initially, it allows programmers to create {\sc sql} statements
using randomized instructions instead of standard keywords.
The modified queries are either reconstructed at runtime using
the same key that is inaccessible to the malicious user,
or the user input is tagged with delimiters that allow
an augmented {\sc sql} grammar to detect the
attack. {\sc sql}rand is one of the few mechanisms that
detect {\sc sql} injection attacks on the database
level (locus $\Omega$).

In the case of {\sc xss} attacks that are based on JavaScript
or {\sc html}, consider a {\sc xor} function that encodes all source of a web
page on the server-side and then, on the client-side, the web browser decodes the
source by applying the same function again (locus {\sc x}).
Variations of this approach include:
{\it Noncespaces}~\cite{GC09} and {\it x{\sc js}}~\cite{APKLM10}
which randomize the instruction set of {\sc html} and
JavaScript respectively.

{\sc isr} is a deterministic approach that can be applied
to detect different attacks in an efficient manner.
However, Sovarel et al.~\cite{SEP05}
have investigated thoroughly the effectiveness
of {\sc isr} and showed that a malicious user
may be able to circumvent {\sc isr} by determining
the randomization key and their results
indicate that doing {\sc isr} in a way that
provides a certain degree of security against a motivated
attacker is more difficult than previously thought.

In the case of Noncespaces, administrators must set
specific policies in a manner similar to a firewall
configuration language. This brings up questions
concerning the diagnostic performance of the mechanism
since the corresponding testing is insufficient
(see Table~\ref{tab:comp}).

Even though the above implementations impose a low
computational overhead, they impose an infrastructure
overhead. In particular, in the case of {\sc sql}rand
the integration of a proxy within the database server
is required while Noncespaces and x{\sc js} require
modifications on both the server and the client.
